### 2016-08-16 doc/manual/version4/inputParameters.tex
v4 Added FourierOption and FourierFactor

\param{saveMatricesAndVectorsInBinary}
{Boolean}
{\false}
{Always}
{If this switch is set to true, the matrix, right-hand-side, and solution vector of the
linear system will be saved in PETSc's binary format.  
The preconditioner matrix will also
be saved if \parlink{useIterativeLinearSolver} == \true.}
These matrices and vectors are not very interesting for routine use of the code,
only for code development and debugging.
Regardless of how this parameter is set,
the physically interesting input and output quantities will be saved in a
separate \HDF~file.

@@

\param{VMECRadialOption}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5.}
{Controls whether the nearest available flux surface in the {\ttfamily vmec wout} file is used, or whether radial interpolation is applied to the \vmec~data
to obtain the magnetic field components on the exact surface requested.\\

@@

\param{Ntheta}
{integer}
{15}
{Always}
{Number of grid points in the poloidal angle. 
This parameter should be odd; see \parlink{forceOddNthetaAndNzeta} in this namelist.
Memory and time requirements DO depend strongly on this parameter.
For stellarator calculations, this parameter can usually be in the range 15-25.
For tokamak calculations at low collisionality, the value of this parameter may need to be higher.}

@@

\param{Nzeta}
{integer}
{15}
{Always}
{Number of grid points in the toroidal angle (per identical segment of the stellarator.)  
This parameter should be odd; see \parlink{forceOddNthetaAndNzeta} in this namelist.
Memory and time requirements DO depend strongly on this parameter.
Set this parameter to 1 for a tokamak calculation.
For stellarator calculations, the value of this parameter required for convergence depends strongly on
the collisionality. At high collisionality, this parameter can be several 10s, depending
on the complexity of $B(\theta,\zeta)$. At low collisionality, this parameter may need to be many 10s or
even $>$ 100 for convergence.
}

@@

\param{Nxi}
{integer}
{16}
{Always}
{Number of Legendre polynomials used to represent the pitch-angle dependence of the distribution function.
Memory and time requirements DO depend strongly on this parameter.
The value of this parameter required for convergence depends strongly on
the collisionality. At high collisionality, this parameter can be as low
as 5. At low collisionality, this parameter may need to be many 10s or
even $>$ 100 for convergence.}

@@

\param{solverTolerance}
{real}
{1e-6}
{Whenever \parlink{useIterativeLinearSolver} == \true}
{
Tolerance used to define convergence of the Krylov solver.
This parameter does not affect memory requirements but it does affect the
time required for solution somewhat.
Occasionally you may want to ease this tolerance to 1e-5 so fewer iterations of the Krylov solver are needed.
}

@@

\param{forceOddNthetaAndNzeta}
{Boolean}
{\true}
{Always}
{
If true, 1 is added to \Ntheta~any time a run is attempted with even \Ntheta,
and 1 is added to \Nzeta~any time a run is attempted with even \Nzeta.
When false, the even and odd grid points are effectively decoupled so results are unstable.
This parameter should be true unless you know what you are doing.
}

@@

\param{thetaDerivativeScheme}
{integer}
{2}
{Always}
{Discretization scheme for the poloidal angle coordinate theta.\\

{\ttfamily thetaDerivativeScheme} = 0: Fourier spectral collocation.  The differentiation matrix in theta is dense.\\

{\ttfamily thetaDerivativeScheme} = 1: Finite differences with a 3 point stencil.  (The differentiation matrix in theta is tridiagonal, aside from the corners.)\\

{\ttfamily thetaDerivativeScheme} = 2: Finite differences with a 5 point stencil.  (The differentiation matrix in theta is pendadiagonal, aside from the corners.).\\

The best value for this parameter is usually 2.}

@@

\param{zetaDerivativeScheme}
{integer}
{2}
{Always}
{Discretization scheme for the toroidal angle coordinate zeta.\\

{\ttfamily zetaDerivativeScheme} = 0: Fourier spectral collocation.  The differentiation matrix in zeta is dense.\\

{\ttfamily zetaDerivativeScheme} = 1: Finite differences with a 3 point stencil.  (The differentiation matrix in zeta is tridiagonal, aside from the corners.)\\

{\ttfamily zetaDerivativeScheme} = 2: Finite differences with a 5 point stencil.  (The differentiation matrix in zeta is pendadiagonal, aside from the corners.).\\

The best value for this parameter is usually 2.}

\param{ExBDerivativeSchemeTheta}
{integer}
{0}
{Whenever the radial electric field is nonzero}
{Options for controlling upwinding of the $\vect{E}\times\vect{B}$ drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}, and are analogous to the options for \parlink{magneticDriftDerivativeScheme}.
This option exists because when the radial electric field is large enough to be comparable to the resonance,
such that the coefficient in front of the $\partial f/\partial \theta$ or $\partial f/\partial\zeta$ terms vanishes near the thermal speed of one of the species,
the distribution function can develop unphysical grid-scale structure.  This option allows upwinding of the $\partial f/\partial\theta$
spatial derivative, which eliminates the grid-scale oscillations.
The parameter \parlink{ExBDerivativeSchemeZeta} serves the same function for the $\partial f/\partial\zeta$ derivative.
\\

{\ttfamily ExBDerivativeSchemeTheta} = 0: Use same differentiation matrices for the $\vect{E}\times\vect{B}$ drift terms as for the parallel streaming term.\\

{\ttfamily ExBDerivativeSchemeTheta} = 1: Treat the $\vect{E}\times\vect{B}$ drift terms using a 4 point upwinded stencil (1 point on 1 side, 2 points on the other.)\\

{\ttfamily ExBDerivativeSchemeTheta} = 2: Treat the $\vect{E}\times\vect{B}$ drift terms using a 5 point upwinded stencil (1 point on 1 side, 3 points on the other.)\\

{\ttfamily ExBDerivativeSchemeTheta} = 3: Treat the $\vect{E}\times\vect{B}$ drift terms using a 6 point upwinded stencil (2 points on 1 side, 3 points on the other.)\\

The different settings require slightly different amounts of memory for factorization due to the different numbers of nonzeros. Option 1 requires the least memory, then 0, then 2,
and 3 requires the most.  The difference in memory required appears to be small, around 10-20\% between settings 1 and 3.
On the other hand, the denser the stencil, the more accurate the result. Hence, in order from least to most accurate, the options are 1, 0, 2, 3.
Option 1 is substantially less accurate than the other options.
You should use the default {\ttfamily ExBDerivativeSchemeTheta} = 0 except for very large radial electric fields, when the electric field is as large as the resonance or larger.
In this case, {\ttfamily ExBDerivativeSchemeTheta} = 3 is recommended.
}

\param{ExBDerivativeSchemeZeta}
{integer}
{0}
{Whenever the radial electric field is nonzero}
{This parameter behaves exactly like \parlink{ExBDerivativeSchemeTheta}, except it applies to the $\zeta$ coordinate instead of $\theta$.}

\param{magneticDriftDerivativeScheme}
{integer}
{3}
{Whenever \parlink{magneticDriftScheme} is nonzero}
{Options for controlling upwinding of the magnetic drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}, and are analogous to the options for \parlink{ExBDerivativeSchemeTheta}.
This option exists because when magnetic drift terms involving $\partial f/\partial \theta$ and $\partial f/\partial\zeta$
are implemented using the same centered difference stencil as the parallel streaming term,
the distribution function can develop unphysical grid-scale structure.  This option allows upwinding of these spatial derivatives, which eliminates the grid-scale oscillations.\\

{\ttfamily magneticDriftDerivativeScheme} = 0: Use same differentiation matrices for the magnetic drift terms as for the parallel streaming term.\\

{\ttfamily magneticDriftDerivativeScheme} = 1: Treat the magnetic drift terms using a 4 point upwinded stencil (1 point on 1 side, 2 points on the other.)\\

{\ttfamily magneticDriftDerivativeScheme} = 2: Treat the magnetic drift terms using a 5 point upwinded stencil (1 point on 1 side, 3 points on the other.)\\

{\ttfamily magneticDriftDerivativeScheme} = 3: Treat the magnetic drift terms using a 6 point upwinded stencil (2 points on 1 side, 3 points on the other.)\\

The different settings require slightly different amounts of memory for factorization due to the different numbers of nonzeros. Option 1 requires the least memory, then 0, then 2,
and 3 requires the most.  The difference in memory required appears to be small, around 10-20\% between settings 1 and 3.
On the other hand, the denser the stencil, the more accurate the result. 
Hence, in order from least to most accurate, the options are 1, 0, 2, 3. Option 1 is substantially less accurate than the other options.
The default setting of 3 is robust and recommended in most cases.
}

@@

\param{useIterativeLinearSolver}
{Boolean}
{\true}
{Always}
{If false, a sparse direct solver
will be used. The direct solver is faster for small (i.e. low-resolution) problems and always yields a solution
(as long as there is sufficient memory).
For large (high resolution) problems, the iterative solver will usually be faster and will use much
 less memory, but it may not always converge.
}

@@

\param{preconditioner\_species}
{integer}
{1}
{Whenever \parlink{useIterativeLinearSolver} = \true~and there are 2 or more species.}
{\\
{\ttfamily preconditioner\_species} = 0: Keep all coupling between species.\\

@@

\param{preconditioner\_x}
{integer}
{1}
{Whenever \parlink{useIterativeLinearSolver} = \true~and \parlink{RHSMode} = 1 or 2.}
{\\
{\ttfamily preconditioner\_x} = 0: Keep full $x$ coupling.\\

@@

\param{preconditioner\_x\_min\_L}
{integer}
{0}
{Whenever \parlink{useIterativeLinearSolver} = \true~and \parlink{RHSMode} = 1 or 2 and \parlink{preconditioner\_x} $>$ 0.}
{The $x$ structure of the matrix will only be simplified for Legendre index $L$ is $\ge$ this value.
Set {\ttfamily preconditioner\_x\_min\_L} = 0 to simplify the matrix for every $L$.
Recommended values are 0, 1, or 2.}

@@

\param{preconditioner\_theta}
{integer}
{0}
{Whenever \parlink{useIterativeLinearSolver} = \true}
{\\
{\ttfamily preconditioner\_theta} = 0: Keep full $\theta$ coupling.\\

{\ttfamily preconditioner\_theta} = 1: Use a 3-point finite difference stencil for $d/d\theta$.\\

{\ttfamily preconditioner\_theta} = 2: Drop all $\theta$ coupling.\\

{\ttfamily preconditioner\_theta} = 3: Replace $d/d\theta$ with the identity matrix.\\

@@

\param{preconditioner\_theta\_min\_L}
{integer}
{0}
{Whenever \parlink{useIterativeLinearSolver} = \true~and \parlink{preconditioner\_theta} $>$ 0.}
{The $\theta$ structure of the matrix will only be simplified for Legendre index $L$ is $\ge$ this value.
Set {\ttfamily preconditioner\_theta\_min\_L} = 0 to simplify the matrix for every $L$.
}

@@

\param{preconditioner\_zeta}
{integer}
{0}
{Whenever \parlink{useIterativeLinearSolver} = \true}
{\\
{\ttfamily preconditioner\_zeta} = 0: Keep full $\zeta$ coupling.\\

{\ttfamily preconditioner\_zeta} = 1: Use a 3-point finite difference stencil for $d/d\zeta$.\\

{\ttfamily preconditioner\_zeta} = 2: Drop all $\zeta$ coupling.\\

{\ttfamily preconditioner\_zeta} = 3: Replace $d/d\zeta$ with the identity matrix.\\

\param{preconditioner\_zeta\_min\_L}
{integer}
{0}
{Whenever \parlink{useIterativeLinearSolver} = \true~and \parlink{preconditioner\_zeta} $>$ 0.}
{The $\zeta$ structure of the matrix will only be simplified for Legendre index $L$ is $\ge$ this value.
Set {\ttfamily preconditioner\_zeta\_min\_L} = 0 to simplify the matrix for every $L$.
}

\param{preconditioner\_xi}
{integer}
{1}
{Whenever \parlink{useIterativeLinearSolver} = \true}
{\\
{\ttfamily preconditioner\_xi} = 0: Keep full $\xi$ coupling.\\

@@

\param{preconditioner\_magnetic\_drifts\_max\_L}
{integer}
{2}
{Whenever \parlink{useIterativeLinearSolver} = \true and \parlink{magneticDriftScheme}$>0$}
{Maximum Legendre mode number for which the poloidal and toroidal magnetic drift terms are included in the preconditioner.
As this parameter is increased, more memory is required for factorization, but fewer KSP iterations are required.
Setting this parameter to $\ge$ \parlink{Nxi} means that the magnetic drifts are always included in the preconditioner.
Setting this parameter to $<0$ means the magnetic drifts are never included in the preconditioner.
The default value should be good.}

>>>>

\param{saveMatricesAndVectorsInBinary}
{Boolean}
{\false}
{Always}
{If this switch is set to true, the matrix, preconditioner matrix, right-hand-side, and solution vector of the
linear system will be saved in PETSc's binary format.  
These matrices and vectors are not very interesting for routine use of the code,
only for code development and debugging.
Regardless of how this parameter is set,
the physically interesting input and output quantities will be saved in a
separate \HDF~file.
}

@@

\param{VMECRadialOption}
{integer}
{0}
{Only when \parlink{geometryScheme} == 5.}
{Controls whether the nearest available flux surface in the {\ttfamily vmec wout} file is used, or whether radial interpolation is applied to the \vmec~data
to obtain the magnetic field components on the exact surface requested.\\

@@

\param{NFourier}
{integer}
{10}
{Always}
{Number of Fourier modes in the poloidal and toroidal angles used to represent the distribution function.
Memory and time requirements DO depend strongly on this parameter.
The value of this parameter required for convergence depends strongly on
the collisionality, with higher values required at low collisionality.
}

@@

\param{mmax}
{integer}
{32}
{Always}
{Determines the maximum poloidal mode number $m$ which can be included: $m \le${\ttfamily mmax}. Memory and time requirements do not depend strongly on this parameter.
}

@@

\param{nmax}
{integer}
{32}
{Always}
{Determines the maximum toroidal mode number $n$ which can be included: $|n|/${\ttfamily Nperiod}$\le${\ttfamily nmax}. Memory and time requirements do not depend strongly on this parameter.
To force a calculation to be axisymmetric, set {\ttfamily nmax} = 0.
}

\param{Nxi}
{integer}
{16}
{Always}
{Number of Legendre polynomials used to represent the pitch-angle dependence of the distribution function.
Memory and time requirements DO depend strongly on this parameter.
The value of this parameter required for convergence depends strongly on
the collisionality. At high collisionality, this parameter can be as low
as 5. At low collisionality, this parameter may need to be many 10s or
even $>$ 200 for convergence.}

@@

\param{solverTolerance}
{real}
{1e-6}
{Always}
{
Tolerance used to define convergence of the Krylov solver.
This parameter does not affect memory requirements but it does affect the
time required for solution somewhat.
Occasionally you may want to ease this tolerance to 1e-5 so fewer iterations of the Krylov solver are needed.
}

@@

@@

\param{FourierOption}
{integer}
{2}
{Whenever \parlink{nmax}$>$0, i.e. whenever the calculation is nonaxisymmetric.}
{Option for choosing which spatial Fourier modes will be included.\\

{\ttfamily FourierOption} = 0: Include all Fourier modes satisfying $|n|/${\ttfamily Nperiod}$\le $\parlink{nmax} and $|m| \le$\parlink{mmax}.
In this case, the input value of \parlink{NFourier} will be ignored, and \parlink{NFourier} will be set to 
\parlink{mmax}$\times(2\times$\parlink{nmax}$+1)+$\parlink{nmax}$+1$.\\

{\ttfamily FourierOption} = 1: Include the first \parlink{NFourier} modes ranked by $m^2+[n/(${\ttfamily Nperiod}$\times$\parlink{FourierFactor}$)]^2$.\\

{\ttfamily FourierOption} = 2: Include the first \parlink{NFourier} modes ranked by the spectrum
of $B^\alpha$ for various powers $\alpha$.
}

@@

\param{FourierFactor}
{real}
{1.0}
{Whenever \parlink{FourierOption}=1 and \parlink{nmax}$>0$.}
{Scales the aspect ratio of the ellipse in $(m,n)$ space for the spatial Fourier modes to include.
The modes are ranked by $m^2+[n/(${\ttfamily Nperiod}$\times$\parlink{FourierFactor}$)]^2$.}

@@

@@

\param{preconditioner\_species}
{integer}
{1}
{Whenever there are 2 or more species.}
{\\
{\ttfamily preconditioner\_species} = 0: Keep all coupling between species.\\

@@

\param{preconditioner\_x}
{integer}
{1}
{Whenever \parlink{RHSMode} = 1 or 2.}
{\\
{\ttfamily preconditioner\_x} = 0: Keep full $x$ coupling.\\

@@

\param{preconditioner\_x\_min\_L}
{integer}
{0}
{Whenever \parlink{RHSMode} = 1 or 2 and \parlink{preconditioner\_x} $>$ 0.}
{The $x$ structure of the matrix will only be simplified for Legendre index $L$ is $\ge$ this value.
Set {\ttfamily preconditioner\_x\_min\_L} = 0 to simplify the matrix for every $L$.
Recommended values are 0, 1, or 2.}

@@

\param{preconditioner\_Fourier}
{integer}
{0}
{Always}
{\\
{\ttfamily preconditioner\_Fourier} = 0: Keep full coupling in the toroidal and poloidal angles.\\

{\ttfamily preconditioner\_Fourier} = 1: Drop some coupling in the toroidal and poloidal angles.\\

@@

\param{preconditioner\_Fourier\_min\_L}
{integer}
{0}
{Whenever \parlink{preconditioner\_Fourier} $>$ 0.}
{The Fourier structure of the matrix will only be simplified for Legendre index $L$ is $\ge$ this value.
Set {\ttfamily preconditioner\_Fourier\_min\_L} = 0 to simplify the matrix for every $L$.
}

@@

\param{preconditioner\_xi}
{integer}
{1}
{Always}
{\\
{\ttfamily preconditioner\_xi} = 0: Keep full $\xi$ coupling.\\

@@
